---
name: Jose
surname: Storopoli
qualifications: PhD
position: "Associate Professor"
address: "Universidade Nove de Julho - UNINOVE - São Paulo - Brazil"
profilepic: pic.png
phone: +55 11 3385-9219
www: storopoli.github.io
email: "josees@uni9.pro.br"
twitter: JoseStoropoli
github: storopoli
linkedin: storopoli
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(vitae)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
orcid_data <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0002-0559-5176")$`0000-0002-0559-5176`$`affiliation-group`$summaries
) %>% select_if(function(x){!all(is.na(x))})
```

# Professional Summary

 * Chief Data Scientist, Associate Professor and Researcher at Universidade Nove de Julho - UNINOVE located in São Paulo - Brazil.
 * Teaches undergraduate and graduate courses in Statistics, Bayesian Statistics, Machine Learning, Deep Learning and Data Science using R, Python and Julia.
 * Researches, publishes and advises PhD candidates on topics about Smart Cities and Urban Planning.
 * Certified RStudio Tidyverse Instructor

# Education

```{r education}
orcid_data %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
```

# Courses

```{r courses}
tibble::tribble(
  ~name, ~year,  ~link, ~language,
  "Ciência de Dados - Data Science", 2020L, "https://github.com/storopoli/ciencia-de-dados", "Python",
  "Estatística - Statistics", 2019L, "https://storopoli.github.io/Estatistica", "R",
  "Estatística Bayesiana - Bayesian Statistics", 2020L,  "https://storopoli.github.io/Estatistica-Bayesiana", "R and RStan"
) %>% 
  detailed_entries(
    what = language,
    when = year,
    with = name,
    why = link
  )
```

# Talks

```{r talks}
tibble::tribble(
  ~title, ~link, ~year,
  "Qual é o papel das universidades no desenvolvimento de cidades inteligentes e sustentáveis?", "https://youtu.be/BAqBTlfBvP8", 2019L,
  "O que é a Ciência de Dados", "https://youtu.be/08uZiJSX_0E", 2020L,
  "Ensinando Data Science no Ensino Superior com Python", "https://youtu.be/Aktd_TFYhvI", 2020L,
  "Gestão urbana e o papel da ciência de dados", "https://youtu.be/qS3xT1e-3F4", 2020L,
  "Vida familiar durante la pandemia del coronavirus en América Latina", "https://youtu.be/0thhpSKt5BM", 2020L
) %>% 
  detailed_entries(
    what = title,
    when = year,
    why = link
  )
```


# Software

```{r softwares}
pkgsearch::ps("Storopoli",size = 100) %>%
  filter(map_lgl(package_data, ~ grepl("Storopoli", .x$Author, fixed = TRUE))) %>% 
  as_tibble() %>%
  detailed_entries(
    with = package,
    what = title, 
    when = lubridate::year(date),
    why = downloads_last_month
  )
```

# Certifications

```{r certifications}
tibble::tribble(
                            ~certification,               ~issuer, ~year,
      "Tidyverse Instructor Certification",             "RStudio", 2020L,
  "Generative Adversarial Networks (GANs)",            "Coursera", 2020L,
               "Machine Learning Engineer",             "Udacity", 2020L,
                     "Python Data Analyst",            "DataCamp", 2019L,
                       "Python Programmer",            "DataCamp", 2018L,
                        "R Data Scientist",            "DataCamp", 2018L,
               "Improving Neural Networks",            "Coursera", 2018L,
       "Neural Networks and Deep Learning",            "Coursera", 2018L,
                        "Machine Learning", "Stanford University", 2018L,
      "Structural Equation Modeling (SEM)",                 "FGV", 2018L
  ) %>% 
  detailed_entries(
    what = issuer,
    with = certification,
    when = year
  )

```


# Publications

```{r publications}
scholar::get_publications("xGU7H1QAAAAJ") %>%
  as_tibble() %>% 
  filter(journal != "") %>% 
  detailed_entries(
    what = title,
    with = journal,
    when = year
  )
```
