---
name: Jose
surname: Storopoli
qualifications: PhD
position: "Chief Data Scientist and Associate Professor"
address: "Universidade Nove de Julho - UNINOVE - São Paulo - Brazil"
profilepic: pic.png
phone: +55 11 3385-9219
www: storopoli.io
email: "josees@uni9.pro.br"
twitter: JoseStoropoli
github: storopoli
linkedin: storopoli
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
---

```{r setup, include=FALSE}
library(magrittr)
library(vitae)
library(dplyr)
library(stringr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
orcid_data <- do.call("bind_rows",
  rorcid::orcid_educations("0000-0002-0559-5176")$`0000-0002-0559-5176`$`affiliation-group`$summaries
) %>% dplyr::select_if(function(x) {!all(is.na(x))})
```

# Professional Summary

 * Chief Data Scientist at UUniversidade Nove de Julho - UNINOVE located in São Paulo - Brazil.
 * Associate Professor and Researcher at Universidade Nove de Julho - UNINOVE located in São Paulo - Brazil.
 * Teaches undergraduate and graduate courses in Statistics, Bayesian Statistics, Machine Learning, Deep Learning and Data Science using R, Python, Julia, Stan and Turing.
 * Researches, publishes and advises PhD candidates on topics about Smart Cities and Urban Planning.
 * Certified RStudio Tidyverse Instructor.
 * Former Editor-in-Chief of the [Iberoamerican Journal of Strategic Management (IJSM)](https://periodicos.uninove.br/riae) in 2020.

# Education

```{r education}
orcid_data %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
```

# Courses

```{r courses}
tibble::tribble(
  ~name, ~year,  ~link, ~language,
  "Ciência de Dados - Data Science", 2020L, "https://storopoli.io/ciencia-de-dados", "Python",
  "Estatística - Statistics", 2019L, "https://storopoli.io/Estatistica", "R",
  "Estatística Bayesiana - Bayesian Statistics", 2020L,  "https://storopoli.io/Estatistica-Bayesiana", "R and Stan"
) %>%
  detailed_entries(
    what = language,
    when = year,
    with = name,
    why = link
  )
```

# Certifications

```{r certifications}
tibble::tribble(
                            ~certification,               ~issuer, ~year,
      "Tidyverse Instructor Certification",             "RStudio", 2020L,
  "Generative Adversarial Networks (GANs)",            "Coursera", 2020L,
               "Machine Learning Engineer",             "Udacity", 2020L,
       "Computational Modeling with Julia",       "Julia Academy", 2020L,
                     "Python Data Analyst",            "DataCamp", 2019L,
                       "Python Programmer",            "DataCamp", 2018L,
                        "R Data Scientist",            "DataCamp", 2018L,
               "Improving Neural Networks",            "Coursera", 2018L,
       "Neural Networks and Deep Learning",            "Coursera", 2018L,
                        "Machine Learning", "Stanford University", 2018L,
      "Structural Equation Modeling (SEM)",                 "FGV", 2018L
  ) %>%
  detailed_entries(
    what = issuer,
    with = certification,
    when = year
  )
```


# Talks

```{r talks}
tibble::tribble(
  ~title, ~link, ~year,
  "Stakeholders e Cidades Inteligentes", "https://youtu.be/KoTZazPWpKA", 2021L,
  "Fluência de Dados e Carreira Profissional", "https://youtu.be/nAo1GS82Jv0", 2021L,
  "Vida familiar durante la pandemia del coronavirus en América Latina", "https://youtu.be/0thhpSKt5BM", 2020L,
  "Observatório de Políticas Públicas", "https://www.youtube.com/watch?v=FUSnGUWKZJs", 2020L,
  "Gestão urbana e o papel da ciência de dados", "https://youtu.be/qS3xT1e-3F4", 2020L,
  "Ensinando Data Science no Ensino Superior com Python", "https://youtu.be/Aktd_TFYhvI", 2020L,
  "Inteligência Artificial e Desenvolvimento Urbano Sustentável", "https://youtu.be/QBbgTOHHdZI?t=5631", 2020L,
  "O que é a Ciência de Dados", "https://youtu.be/08uZiJSX_0E", 2020L,
  "Qual é o papel das universidades no desenvolvimento de cidades inteligentes e sustentáveis?", "https://youtu.be/BAqBTlfBvP8", 2019L
) %>%
  detailed_entries(
    what = title,
    when = year,
    why = link
  )
```


# Software

```{r github-contribs, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
today <- lubridate::today()
year_before <- lubridate::as_date(today - lubridate::years(1))
token <- Sys.getenv("GITHUB_PAT")
con <- ghql::GraphqlClient$new(
  url = "https://api.github.com/graphql",
  headers = list(Authorization = paste0("Bearer ", token))
)
qry <- ghql::Query$new()
query_text <- glue::glue('{user(login: "storopoli") {
    email
    createdAt
    contributionsCollection(from: "<< str_c(year_before, "T00:00:00Z") >>", to: "<< str_c(today, "T00:00:00Z")>> ") {
      contributionCalendar {
        totalContributions
      }
    }
  }
}', .open = "<<", .close = ">>")
qry$query("mycontrib", query_text)
(contribs <- con$exec(qry$queries$mycontrib))
total_contribs <- jsonlite::fromJSON(contribs)$data$user$contributionsCollection$contributionCalendar$totalContributions
```

* Total GitHub Contributions: `r total_contribs`
* Featured Github Contributions:
  * `NetworkX`: New Panther and Panther++ Fast top-k similarity search on large networks[^1].
  * `Stan`: CI/CD GitHub Actions and Documentation.
  * `SciPy`: Documentation.

[^1]: Zhang, J., Tang, J., Ma, C., Tong, H., Jing, Y., & Li, J. (2015). Panther: Fast top-k similarity search on large networks. In Proceedings of the ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (Vol. 2015-August, pp. 1445–1454). Association for Computing Machinery. https://doi.org/10.1145/2783258.2783267

```{r softwares}
pkgsearch::ps("Storopoli", size = 100) %>%
  filter(purrr::map_lgl(package_data, ~ grepl("Storopoli", .x$Author, fixed = TRUE))) %>%
  dplyr::as_tibble() %>%
  detailed_entries(
    with = package,
    what = title,
    when = lubridate::year(date),
    why = downloads_last_month
  )
```

# Publications

```{r publications}
scholar::get_publications("xGU7H1QAAAAJ") %>%
  dplyr::as_tibble() %>%
  filter(journal != "") %>%
  detailed_entries(
    what = title,
    with = journal,
    when = year
  )
```
